Containers and R---the Rockerverse and beyond

### 2019-11-06 manuscript.Rmd
one sentence per line, fix remaining bullet points in common envs section

  - [`repo2docker`](https://repo2docker.readthedocs.io/en/latest/config_files.html) (`install.R`, `DESCRPTION`, `runtime.txt`) based on the Rocker images [@nuest]
- GPU [@noamross, @cboettig]

One use for containers is to run on shared local hardware where teams manage
their own high-performance servers  This can follow one of several
design patterns: users may deploy containers to hardware as a work environment
for a specific project, conatiners may provide per-user persistent environments, or a single container can act as
a common multi-user environment for a server.  The former models provide modularity,
while the latter approach is most similar to a simple shared server. In all cases,
though, the containerized approach provides several advantages: First, users may
use the same image and thus work environment on desktop and laptop computers, as well.
Second, software updates can be achieved by updating and redeploying the container,
rather than tracking local installs on each server.  Third, the containerized
environment can be quickly deployed to other hardware, cloud or local, if 
more resources are neccessary or in case of server destruction or failure. In any of
these cases, users need a method to interact with the containers, be it and
IDE, or command-like access and tools such as SSH, which is usually not part
of standard container recipes and must be added.  The Rocker project provides
containers pre-installed with the RStudio IDE.

@@

- Gigantum stack

@@

- [RCloud](https://github.com/att/rcloud/tree/master/docker) ?

>>>>

One use for containers is to run on shared local hardware where teams manage their own high-performance servers.
This can follow one of several design patterns: users may deploy containers to hardware as a work environment for a specific project, conatiners may provide per-user persistent environments, or a single container can act as a common multi-user environment for a server.
The former models provide modularity, while the latter approach is most similar to a simple shared server.
In all cases, though, the containerized approach provides several advantages: First, users may use the same image and thus work environment on desktop and laptop computers, as well.
Second, software updates can be achieved by updating and redeploying the container, rather than tracking local installs on each server.
Third, the containerized environment can be quickly deployed to other hardware, cloud or local, if more resources are neccessary or in case of server destruction or failure.
In any of these cases, users need a method to interact with the containers, be it and IDE, or command-like access and tools such as SSH, which is usually not part of standard container recipes and must be added.
The Rocker project provides containers pre-installed with the RStudio IDE.

@@

@@

[RCloud](https://github.com/att/rcloud/tree/master/docker) uses a `rocker/drd` base image for creation of collaborative data analysis and visualisation environments.
